*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-20 Code/Manuscript_O2.Rmd
Added protein quantification to Methods and materials

---
title: "*Prochlorococcus marinus* responses to light and oxygen" 
author:
  - name: '**Mireille Savoie**'
    affil: 1
    main: true
    email: msavoie@mta.ca
  - name: Aurora Mattison
    affil: 1, 2
  - name: Julie Nadeau
    affil: 1
  - name: Laurel Genge
    affil: 1
  - name: Sylwia Śliwińska-Wilczewska
    affil: 1
  - name: Maximilian Berthold
    affil: 1, 3
  - name: Naaman Omar
    affil: 1
  - name: Ondřej Prášil
    affil: 1, 4
    main: false
  - name: Amanda M. Cockshutt
    affil: 1, 5
    main: false
  - name: Douglas A. Campbell
    affil: 1
    main: false
    orcid: '0000-0001-8996-5463'
    email: 'dcampbel@mta.ca'
affiliation:
  - num: 1
    address: Department of Biology, Mount Allison University
institute:
  - mta: 'Department of Biology, Mount Allison University, 63B York St., Sackville NB, Canada, E4L 1G7.'
  - num: 2
  - ubc: 'Department of Biology, University of British Columbia'
  - num: 3
  - umwelt: 'Umweltbundesamtm, Dessau-Roßlau, Germany'
  - num: 4
  - alga: 'Algatech, Czech Academy of Science'
  - num: 5
  - sfx: 'Department of Chemistry, St. Frances Xavier University'
date: "`r format(Sys.Date())`"
output:
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::word_document2:
    code_folding: show
    reference_docx: KnitTemplate.docx
    keep_md: yes
    toc: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
always_allow_html: true
bibliography: [Manuscript_O2.bib, RPackages.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

### Estimation of Photosynthetically Usable Radiation {.unnumbered}

To calculate the Photosynthetic Usable Radiation (PUR), a proxy of photons absorbed, for each ecotype
of *P. marinus*, the imposed Photosynthetic Active
Radiation (PAR) was first determined. An emission profile of each colored LED
light of the MCMIX-OD Multicultivator and the white LED light of the MC1000-OD Multicultivator was obtained using a Jaz spectrometer (Ocean Optics, Inc.,Dunedin FL, USA) equipped with a fiber
optic cable, HH2 FiberOpticJmp (Part number A901073, Malvern Panalytical
Ltd, Malvern, UK) and scanned to measure the emission wavelengths from 200 nm to 1000 nm. Following the determination of PAR, an *in-vivo* whole cell absorbance spectrum for each *P. marinus* was obtained using the Olis 14 UV/VIS Clarity
Spectrophotometer (Olis Inc, Bogart, Georgia) by scanning across the visible spectral range of λ = 350 nm to 750 nm at 1 nm intervals. The 20 cm path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra. Whole cell absorbance spectra were measured for each strain under each imposed spectral waveband.

@@

The applied photoperiod was administered using a sinusoidal function to simulate light levels equivalent to sun rise and sunset. The area under a sine curve is equivalent to a triangle, therefore the equation to determine the cumulative diel absorbed PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) equation \@ref(eq:SumPURDay).

@@

### Protein Immunoblot {.unnumbered}

XXX Mireille to confirm and summarise XXX
Samples were thawed and placed in FastPrep lysing vials with 500 uL of 1X Protein Extraction Buffer (PEB). Cells were lysed for 3 cycles of 60 seconds at 6.5m s-1 with 60 second intervals on ice between cycles.  The lysing vials were centrifuged at 16100g for 5 minutes, the supernatant was transferred to a 600 uL microcentrifuge tube and centrifuged again at 16100g for 3 minutes.  40uL of the supernatant were subsampled into labeled vials and stored in  -80 oC freezer until analysis. The bicinchoninic acid assay (BCA) was used for total protein determination using a calibration curve of bovine gamma globulin (BGG) standard in the 0 to 1.0 mg/mL range.

All samples and appropriate standards were prepared as described in [@brownFluxCapacitiesAcclimation2008] and loaded onto either 15 or 17 well Invitrogen Bolt 4-12% Bis-Tris gels.  All sample extract loads were calculated based on 2.0 ug of total protein.  All gels were run for 25 minutes at 200V and transferred for 60 minutes at 20V onto a PVDF membrane.  Blots were blocked overnight in 2% ECL blocking solution made with 1XTBS-T, the exception being target protein Fcp6 which was not blocked.  Fcp6 was incubated overnight with 1:5000 dilution of primary antibody (obtained by J. Lavaud) in 2% ECL blocking solution directly after transfer.  The following morning, each blot was incubated in their appropriate antibody and agitated gently on a rotator table for 1 hour at room temperature.   Dilution of primary antibodies was  PsbA 1:10000 (Agrisera,  AS05 084), and RbcL 1:10000 (Agrisera,  AS03037).   Each blot was washed with 10mL of 1XTBS-T. Two times briefly preceded by 15 minutes on a rotator table, followed by three times for 5 minutes on the rotator table.  All blots were incubated in a 1:15000 dilution of secondary antibody (anti-rabbit HRP Biorad lot 64230791) and agitated gently on a rotator table for 1 hour at room temperature.   All blots were washed as per the wash protocol described above.  Blots were incubated in Amersham ECL Select chemiluminescent substrate and imaged in a Biorad VersaDoc imager.

Target protein standards were loaded at 3 concentrations to establish a calibration curve.  PsbA standard (Agrisera, AS01 016S) range 12.5 - 100 fmol per lane and RbcL standard (Agrisera, AS01 017S) range 175 - 1400 fmol per lane.

>>>>

---
title: "*Prochlorococcus marinus* responses to light and oxygen" 
author:
  - name: '**Mireille Savoie**'
    affil: 1
    main: true
    email: msavoie@mta.ca
  - name: Aurora Mattison
    affil: 1, 2
  - name: Julie Nadeau
    affil: 1
  - name: Laurel Genge
    affil: 1
  - name: Sylwia Śliwińska-Wilczewska
    affil: 1
  - name: Maximilian Berthold
    affil: 1, 3
  - name: Naaman Omar
    affil: 1
  - name: Ondřej Prášil
    affil: 1, 4
    main: false
  - name: Amanda M. Cockshutt
    affil: 1, 5
    main: false
  - name: Douglas A. Campbell
    affil: 1
    main: false
    orcid: '0000-0001-8996-5463'
    email: 'dcampbel@mta.ca'
affiliation:
  - num: 1
    address: Department of Biology, Mount Allison University
institute:
  - mta: 'Department of Biology, Mount Allison University, 63B York St., Sackville NB, Canada, E4L 1G7.'
  - num: 2
  - ubc: 'Department of Biology, University of British Columbia'
  - num: 3
  - umwelt: 'Umweltbundesamtm, Dessau-Roßlau, Germany'
  - num: 4
  - alga: 'Algatech, Czech Academy of Science'
  - num: 5
  - sfx: 'Department of Chemistry, St. Frances Xavier University'
date: "`r format(Sys.Date())`"
output:
  bookdown::word_document2:
    code_folding: show
    reference_docx: KnitTemplate.docx
    keep_md: yes
    toc: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
  bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
    pandoc_args: 
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
always_allow_html: true
bibliography: [Manuscript_O2.bib, RPackages.bib]
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

@@

### Estimation of photosynthetically usable radiation {.unnumbered}

To calculate the Photosynthetic Usable Radiation (PUR), a proxy of photons absorbed, for each *P. marinus* ecotype, the imposed Photosynthetic Active
Radiation (PAR) was first determined. An emission profile of each colored LED
light of the MCMIX-OD Multicultivator and the white LED light of the MC1000-OD Multicultivator was obtained using a Jaz spectrometer (Ocean Optics, Inc.,Dunedin, FL, USA) equipped with a fiber
optic cable, HH2 FiberOpticJmp (Part number A901073, Malvern Panalytical
Ltd, Malvern, UK) and scanned to measure the emission wavelengths from 200 nm to 1000 nm. Following the determination of PAR, an *in-vivo* whole cell absorbance spectrum for each *P. marinus* was obtained using the Olis 14 UV/VIS Clarity
Spectrophotometer (Olis Inc, Bogart, GA, USA) by scanning across the visible spectral range of λ = 350 nm to 750 nm at 1 nm intervals. The 20 cm path length of the internally reflective cavity of the Olis spectrophotometer was corrected to a 1 cm path length using the Javorfi correction method [@javorfiQuantitativeSpectrophotometryUsing2006] on PRO 99 media subtracted whole cell absorbance spectra. Whole cell absorbance spectra were measured for each strain under each imposed spectral waveband.

@@

The applied photoperiod was administered using the sine circadian light function of the PSI Multicultivator to simulate light exposure approximating sun rise through to sunset. The area under a sine curve is approximately equivalent to the area of a triangle, therefore the equation to determine the cumulative diel absorbed PUR (µmol photons m^-2^ d^-1^) is one half of the base (photoperiod) multiplied by the height (PUR) (equation \@ref(eq:SumPURDay)),

@@

### Quantitative protein immunoblotting {.unnumbered}

XXX Mireille to confirm and summarise XXX

Quantitative protein immunoblots were used to determine the concentrations of 5 target proteins; FtsH, PsbA, PetC, PsaC and RbcL in *P. marinus* MED4 and MIT9313 cultures grown in the PSI Multicultivator under imposed PAR light levels of 30 and 100 µmol photons m^-2^ s^-1^, spectral wavebands of 660 and 450 nm and [O~2~] of 2.5 and 250 µM. 40 mL of culture were transferred into a 50 mL falcon tube and 40 µL of 10 % Pluronic F68 acid was added to the cell suspension. The cell suspension was centrifuged for 30 minutes at 17664 g using a J-26XP centrifuge (Beckman Coulter, Brea, CA, USA) equipped with a J-10 rotor. The supernatant was removed and the resulting pellet was flash frozen in liquid nitrogen and stored at -80 °C for later use.

Protein samples were thawed and placed in 2 mL FastPrep®-24 bead lysing matrix D vials (MP Biomedicals, Irvine, CA, USA; SKU 116913050) with 200 uL of 1X protein extraction buffer (0.0281 mol L^−1 TRIS base buffer, 0.0211 mol L^−1 TRIS HCl buffer, 0.0735 mol L^−1 lithium dodecyl sulfate, 1.08 mol L^−1 glycerol, 0.5 mmol L^−1 ethylenediaminetetraacetic acid, 0.1 mg·mL−1 PefaBloc SC (AEBSF) protease inhibitor) [@brownFluxCapacitiesAcclimation2008]  XXX note we used a low tris PEB recipe not sure where it came from XXX. Cells were lysed for 3 cycles of 60 seconds at 6.5m s-1 with 60 second intervals on ice between cycles.  The lysing vials were centrifuged at 16100g for 5 minutes, the supernatant was transferred to a 600 uL microcentrifuge tube and centrifuged again at 16100g for 3 minutes.  40 µL of the supernatant were subsampled into labeled vials and stored at -80 °C until analysis. The bicinchoninic acid (BCA) assay was used for total protein determination using a calibration curve of bovine gamma globulin (BGG; Bio-Rad, Hercules, CA, USA) standard ranging from 0 to 1.0 mg mL^-1 range.

All samples and appropriate standards were prepared as described in [@brownFluxCapacitiesAcclimation2008]. Between 0.1 to 4.0 µg of total protein was loaded onto 15 well Invitrogen Bolt 4-12% acrylamide Bis-Tris gels (ThermoFisher Scientific, Waltham, MA, USA). All gels were run for 25 minutes at 200V using Invitrogen Bolt Mini Gel tanks and Invitrogen Bolt MES SDS running buffer (ThermoFisher Scientific, Waltham, MA, USA) and transferred for 60 minutes at 20V onto a PVDF membrane (Bio-Rad, Hercules, CA, USA; SKU 1620177).  Blots were blocked overnight in 2% ECL blocking solution as described by @brownFluxCapacitiesAcclimation2008. The following morning, each blot was incubated in their appropriate antibody obtained from Agrisera (Vännäs, Sweden; FtsH  1:5,000 dilution, AS11 1789; PsbA  1:10000 dilution, AS05 084; PetC 1:XXXXX dilution, ASXXXXX; PsaC 1:XXXXXX dilution, ASXXXXXXX ; RbcL 1:10000 dilution, AS03 037) and a 1:15000 dilution of the secondary antibody, goat anti-rabbit HRP conjugated (Bio-Rad, Hercules, CA, USA; SKU 1706515, lot 64230791).  Blots were incubated in Amersham ECL Select chemiluminescent substrate (Danaher, Washington, DC, USA) and imaged in a Bio-Rad VersaDoc imager (Bio-Rad, Hercules, CA, USA). Images were quantitated using the ImageJ2 software (version 1.53c).
